Temporal stability in human interaction networks: sector sizes, topological prominence and time activity

### 2015-10-03 paper.tex
incorporada figura melhorada do seccionamento

\begin{figure}[!h]
	\centering
	\includegraphics[width=0.5\textwidth]{figs/fser_}
	\caption{Classification of the scale-free network vertices by comparing the degree
		distribution against that of an Erd\"os-R\'enyi ideal network.
		The latter has more intermediary vertices, while the former has more peripheral and hub vertices.
		The sector borders are defined by the two intersections $k_L$ and $k_R$ of the connectivity distributions.
		Characteristic degrees are in the compact intervals: $[0,k_L]$, $(k_L,k_R]$, $(k_R,k_{max}]$ for the Erd\"os sectors (periphery, intermediary and hubs).}
		\label{fig:setores}
\end{figure}
To ensure statistical validity of the histograms, bins can be chosen to contain at least $\eta$ vertices of the real network. The range $\Delta$ of incident values should be partitioned in $m$ parts $\Delta=\cup_{i=1}^m \Delta_i$, with $\Delta_i\cap \Delta_j \; \forall\; i \neq j$. Thus, $\Delta_i=\{max(\Delta_{i-1})<k\leq j \;\;|\; \sum_{max(\Delta_{i-1})+1}^j \eta_k \geq \eta \text{ and } (\sum_{max(\Delta_{i-1})+1}^{j-1} \eta_k < \eta \text{ or } j=max(\Delta_{i-1})+1) \}$, with $\eta_k$ the number of vertices with degree $k$ and $max(\Delta_{0})=-1$. This changes equation~\ref{criterio} to

>>>>

\begin{figure}[!h]
	\centering
	\includegraphics[width=0.5\textwidth]{figs/fser__}
	\caption{Classification of vertices by comparing the degree
		distributions.
		The binomial distribution of the Erd\"os R\'enyi network exhibit more intermediary vertices, while a scale-free network, associated with the power-law distribution,
		has more peripheral and hub vertices.
		The sector borders are defined with respect to the intersections of the distributions.
Characteristic degrees are in the compact intervals: $[0,k_L]$, $(k_L,k_R]$, $(k_R,k_{max}]$ for the periphery, intermediary and hubs sectors (the ``Erd\"os sectors'').
		The empirical distributions of connectivity in interaction networks, e.g. derived from email lists,
		can be sectioned by comparison with to the associated binomial distribution.
		In this figure, a snapshot of 1000 messages from CPP list yield the degree distribution
		of an interaction network of 98 nodes and 235 edges.
		A throughout exposition of the method is exposed in Section~\ref{sectioning}.}
		\label{fig:setores}
\end{figure}
To ensure statistical validity of the histograms, bins can be chosen to contain at least $\eta$ vertices of the real network. The range $\Delta$ of incident values should be partitioned in $m$ parts $\Delta=\cup_{i=1}^m \Delta_i$, with $\Delta_i\cap \Delta_j \; \forall\; i \neq j$. Thus, $\Delta_i=\{max(\Delta_{i-1})<k\leq j \;\;|\; \sum_{max(\Delta_{i-1})+1}^j \eta_k \geq \eta \text{ and } (\sum_{max(\Delta_{i-1})+1}^{j-1} \eta_k < \eta \text{ or } j=max(\Delta_{i-1})+1) \}$, with $\eta_k$ the number of vertices with degree $k$ and $max(\Delta_{0})=-1$. This changes equation~\ref{criterio} to
